A neural coarse graining theory of consciousness/\newline Non-trivial Informational closure through neural coarse-graining as the Fundamental Informational Correlates of Consciousness

### 2019-04-23 Paper_neural_coarse_graining_of_consciousness.tex
add something in chapter 4 beginning

        \rewording{informational closure also suggests that there is no information flow from the lower to the higher level. Knowledge of the microscopic levels will not improve predictions of the future states of the macroscopic levels \citep{PFANTE.2014}}. This indicates that informational closed macroscopic levels can be treated as a complete reality.

>>>>

        \rewording{informational closure also suggests that there is no information flow from the lower to the higher level. Knowledge of the microscopic levels will not improve predictions of the future states of the macroscopic levels \citep{PFANTE.2014}}. 
        Information closure also implies that the system is ignorant of information outside of the system. Therefore, if a coarse-grained level achieves information closure, it suggests the NTIC process at the coarse-grained level is ignorant of information processing happening at microscopic levels and also higher coarse-grained levels. This virtually makes the informational closed macroscopic levels as a complete reality. 
        \todo{Due to my concern mentioned last week, I think I should also mention the closure is not only to the environment but also to the microscopic levels}
